
---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# codeBase

# Introduction

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include =TRUE)
```

```{r Load Library, include=FALSE}
library(codeBase)
library(tidyverse)
library(checkmate)
library(magrittr)
library(data.table)
library(testthat)
library(knitr)
```

```{r, echo = FALSE, include = FALSE}
sessionInfo()
```

## What functions are included in the package?

Currently the master branch contains the following functions however we have many others as pull request
```{r Package Functions}
ls("package:codeBase")
```

# Using the Package

## Import 'Predicting Household Sale Prices' dataset

Importing the packages inbuilt testing datasets
```{r Import data}
data(hh_train)
data(hh_test)
```

This data is the Californian house prices dataset and has a target of `r "SalePrice"`

```{r process data, include=FALSE}
target <- 'SalePrice'
hh_train %<>% select(all_of(c(intersect(names(hh_train), names(hh_test)), target)))
hh_test %<>% select(intersect(names(hh_train), names(hh_test)))
names(hh_train)
```

## Data Exploration

### expl_na
For each variable, find the number or percentage of NA's in a dataset
```{r expl_na}
na_vars <- codeBase::expl_na(df = hh_train, na.strings = NULL, ignore.case = FALSE) 
```


We can now see that we have some factors which are useless as they are mostly unknown:
```{r echo=TRUE}
head(dplyr::arrange(na_vars, -na)) %>% kable()
```

### expl_categorical
For each categorical variable, find the number of / percentage of each level
```{r expl_categorical}
codeBase::expl_categorical(df = hh_train, char.level = 3, num.level =2)  %>% kable()
```

This format can be easily plotted to show factor distributions for each factor (either in a loop or using ggplot2 facet functions)

### expl_summary
Find the mean, standard deviation, length, and NA count of numeric and integer variables, with the option to group by other variables
```{r expl_summary}
codeBase::expl_summary(hh_train, summarise_vars = "SalePrice", group_vars = "YrSold") %>% kable()
```

### encode_freq
Apply frequency encoding with the option to group the rarest levels
```{r include=TRUE}
# Add some unknowns to show what it looks like
hh_train$Neighborhood[5:10] <- NA
```

From the below output we can see that the factor Neighborhood has more levels than can usefully be modelled
```{r encode_freq}
hh_train %>% group_by(Neighborhood) %>% summarise(Volume = n()) %>% kable()
```

We decide to frequency encode the factor

```{r echo=TRUE}
nhood_freq <- codeBase::encode_freq(data = hh_train$Neighborhood, 
                                n_levels = 5, 
                                min_level_count = NULL, 
                                unknown_levels = NULL,
                                unknown_treatment_method = 1)
```

which gives us with the transformed factor

```{r echo=TRUE}
hh_train$nhood_freq <- factor(x = nhood_freq$data, labels = nhood_freq$levels)
hh_train %>% group_by(nhood_freq) %>% summarise(Volume = n()) %>% kable()
```

## Build a Model

We build a model using standard R functions
```{r regression, include=TRUE}
hh_train %<>% mutate(GarageYrBlt = coalesce(GarageYrBlt, YearBuilt))
model_vars <- c('GarageYrBlt', 'nhood_freq', 'OverallCond', 'ExterCond', target)
hh_train %<>% select(all_of(model_vars))
model <- stats::glm(formula = 'SalePrice ~ .',
                   family = 'gaussian',
                   data = hh_train)
summary(model)
hh_train$pred <- predict(object = model, newdata = hh_train)
```

## Model Evaluation

### plot_PDP

We can now plot PDP plots for any factor
```{r plot_PDP, warning=FALSE}
codeBase::plot_PDP(data = hh_train,
               model = model,
               explain_col = 'GarageYrBlt',
               n_bins = 20,
               use_plotly = FALSE)
```


### plot_PDP for 2 factors

We can also plot pairs of factors
```{r plot_2D_PDP}
codeBase::plot_PDP(data = hh_train,
               model = model,
               explain_col = c('GarageYrBlt', 'OverallCond'),
               n_bins = 10,
               use_plotly = FALSE)
```

Note:
OverallCond: Rates the overall condition of the house
10 - Very Excellent
1 - Very Poor

### plot_ALE

We can now plot ALE plots for any factor
```{r plot_ALE}
codeBase::plot_ALE(data = hh_train,
               model = model,
               explain_col = 'GarageYrBlt',
               n_bins = 20,
               use_plotly = FALSE)
```



### plot_lift_curve

We can also plot useful global model outputs such as lift curves
```{r plot_lift_curve_plotly}
codeBase::plot_lift_curve(actual = hh_train$SalePrice,
                      predicted = hh_train$pred,
                      use_plotly = FALSE)
```

### plotly vs ggplot2

Some users may require plotly and others ggplot2 so all plots work with both engines. This can be controlled with the `use_plotly` parameter of the plotting functions.

## Metrics

We have many metrics all of which have the same construction of arguments meaning they can be used by other functions or in loops


```{r multiple metrics}

codeBase::metric_rmse(actual = hh_train$SalePrice, predicted = hh_train$pred)
codeBase::metric_mae(actual = hh_train$SalePrice, predicted = hh_train$pred)

codeBase::metric_deviance(actual = hh_train$SalePrice, predicted = hh_train$pred, family = "gaussian")
codeBase::metric_nloglik(actual = hh_train$SalePrice, predicted = hh_train$pred, family = "gaussian")

```
